From Light to Growth: A Study of Night-Time Light as an Indicator of Economic Development

### 2024-11-24 paper/paper.qmd
made some changes to the QMD.

The main task in preparing the dataset was the extraction of night-time light (NTL) intensity values from the GeoTIFF files. Using the `rasterio` package in Python, we processed annual TIFF files to extract Digital Number (DN) values, which represent the intensity of light, along with their corresponding latitude and longitude coordinates. This provided a spatial dataset that detailed the distribution of NTL intensity globally for each year.

@@

>>>>

The main task in preparing the dataset was the extraction of night-time light (NTL) intensity values from the GeoTIFF files. Using the 'Rasterio' package [@raster] in Python, we processed annual TIFF files to extract Digital Number (DN) values, which represent the intensity of light, along with their corresponding latitude and longitude coordinates. This provided a spatial dataset that detailed the distribution of NTL intensity globally for each year.

@@

# Reference
